Fast gravitational wave parameter estimation without compromises

### 2023-01-26 src/tex/ms.tex
Reword accelarators

% GPU helps packing a shit ton of waveform evaluation
Another benefit of accelerators is the parallel evaluation of waveforms. Since
the waveform model we use can be evaluated at any given time or frequency
independently, this means computing a waveform can be trivially parallelized
over frequency bins. Together with the heterodyned likelihood, we can evaluate
the likelihood at $\mathcal{O}(10^7)$ different locations on an \textsc{Nvidia}
A100 GPU.  The high throughput of likelihood evaluations unlocks the potential
of the \textsc{flowMC} sampling algorithm.

>>>>

% GPU helps packing a shit ton of waveform evaluation
Another benefit of accelerators is the parallel evaluation of waveforms. Since
the waveform model we use can be evaluated at any given time or frequency
independently, this means computing a waveform can be trivially parallelized
over frequency bins. On an \textsc{Nvidia} A100 GPU, we can evaluate the
waveform model $\sim \mathcal{O}(10^9)$ times in a second for different
frequencies or source parameters. Together with the heterodyned likelihood, this
allows us to run thousands of parallel chains in a PE run. The high throughput
of waveform evaluations unlocks the potential of the \textsc{flowMC} sampling
algorithm.
